The symmetric \textit{Fermi} and eROSITA bubbles problem: A proof-of-concept study

### 2022-01-28 paper.tex
update

  \begin{figure}
      \includegraphics[width=\columnwidth]{figures/fig__numberDensityHistogram.png}
    \caption{The volume filling factor as a function of\
             initial number density within the disk without jet source.\
             The regions covered by vertical bands represent the allowable number densities \citep{peak-ism-density} for\
             hot ionized, warm neutral (WNM), warm ionized (WIM), cold nuetral mediums (CNM), and molecular clouds.}
      \label{fig__numberDensityHistogram}
  \end{figure}

@@

\begin{figure}
  \includegraphics[width=\linewidth]{figures/fig__spectrum.png}
  \caption{
      Simulated spectra of the Fermi bubbles calculated for a longitude range of\
      $l=[-10^{\circ},10^{\circ}]$ for different latitude bins.\
      The gray band represents the observational data of \citet{Ackermann2014}.
  }
  \label{fig__gammaRay}
\end{figure}

>>>>

  \begin{figure}
      \includegraphics[width=\columnwidth]{figures/fig__numberDensityHistogram.png}
    \caption{The volume filling factor as a function of\
             initial number density within the disk without jet source.\
             The vertical bands represent the allowable number densities \citep{peak-ism-density} for\
             hot ionized, warm neutral (WNM), warm ionized (WIM), cold nuetral mediums (CNM), and molecular clouds.}
      \label{fig__numberDensityHistogram}
  \end{figure}

@@

\begin{figure}
  \includegraphics[width=\linewidth]{figures/fig__spectrum.png}
  \caption{
      Simulated gamma-ray spectra (top) of the Fermi bubbles calculated for a longitude range of\
      $|l|<10^{\circ}$ for different latitude bins.\
      The gray band represents the observational data of \citet{Ackermann2014}.\
      Microwave spectra (bottom) averaged over $|l|<10^{\circ}$, $20^{\circ}<|b|<30^{\circ}$.\
      The data point represents the \textit{WMAP} data in the 23 GHz K band and the shaded area indicates the range\
      of synchrotron spectral indices allowed for the \textit{WMAP} haze \citep{Dobler_2008}.
  }
  \label{fig__gammaRay}
\end{figure}
